\documentclass[xcolor={dvipsnames}]{beamer}

% ==========================================
% 1. CONFIGURATION
% ==========================================
\newcommand{\MyTitle}{A Data Structure Perspective to the \\ \small RDD-based Apriori Algorithm on Spark}
\newcommand{\MyShortTitle}{Apriori on Spark}
\newcommand{\MyAuthor}{Luis Alberto Vásquez Vargas}
\newcommand{\MyShortAuthor}{Luis Vásquez}
\newcommand{\MyInstitute}{IC -- UNICAMP} 
\newcommand{\MyDate}{March 31, 2026} 

% --- COLOR PALETTE ---
\definecolor{PrimaryColor}{HTML}{141B41}    % Space Indigo
\definecolor{SecondaryColor}{HTML}{306BAC}  % Ocean Deep
\definecolor{AccentColor}{HTML}{6F9CEB}     % Cornflower Blue
\definecolor{LightAccent}{HTML}{98B9F2}     % Baby Blue Ice
\definecolor{AlertColor}{HTML}{918EF4}      % Soft Periwinkle

% ==========================================
% 2. THEME SETUP
% ==========================================
\mode<presentation>
{
  \usetheme{Madrid}
  \usefonttheme{serif}
  \setbeamertemplate{navigation symbols}{}
  
  % Custom Footer
  \setbeamertemplate{footline}{
    \leavevmode%
    \hbox{%
    \begin{beamercolorbox}[wd=.4\paperwidth,ht=2.25ex,dp=1ex,center]{author in head/foot}%
      \usebeamerfont{author in head/foot}\MyShortAuthor~~\textbar~~\MyInstitute
    \end{beamercolorbox}%
    \begin{beamercolorbox}[wd=.3\paperwidth,ht=2.25ex,dp=1ex,center]{title in head/foot}%
      \usebeamerfont{title in head/foot}\MyShortTitle
    \end{beamercolorbox}%
    \begin{beamercolorbox}[wd=.3\paperwidth,ht=2.25ex,dp=1ex,right]{date in head/foot}%
      \usebeamerfont{date in head/foot}\insertshortdate{}\hspace*{2em}
      \insertframenumber{} / \inserttotalframenumber\hspace*{2ex} 
    \end{beamercolorbox}}%
    \vskip0pt%
  }

  \setbeamercolor{structure}{fg=SecondaryColor}
  \setbeamercolor{palette primary}{bg=PrimaryColor, fg=white}
  \setbeamercolor{palette secondary}{bg=SecondaryColor, fg=white}
  \setbeamercolor{palette tertiary}{bg=AccentColor, fg=white}
  \setbeamercolor{titlelike}{parent=palette primary}
  \setbeamercolor{author in head/foot}{fg=white, bg=PrimaryColor}
  \setbeamercolor{title in head/foot}{fg=white, bg=SecondaryColor}
  \setbeamercolor{date in head/foot}{fg=white, bg=AccentColor}
  \setbeamercolor{block title}{bg=SecondaryColor, fg=white}
  \setbeamercolor{block body}{bg=LightAccent!20, fg=PrimaryColor}
  \setbeamercolor{alerted text}{fg=AlertColor}
} 

\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage{amsmath, amsfonts, amssymb}

\title[\MyShortTitle]{\MyTitle}
\author[\MyShortAuthor]{\MyAuthor}
\institute{\MyInstitute}
\date{\MyDate}

\begin{document}

\begin{frame}
  \titlepage
  \begin{center}
      \footnotesize Professor: Luiz Fernando Bittencourt \\
      \textbf{MO809 -- Tópicos em Computação Distribuída (1s2026)}
  \end{center}
\end{frame}

\begin{frame}{Outline}
  \tableofcontents
\end{frame}

\section{Introduction}
\begin{frame}{The "Bundle Deal" Strategy}
    Imagine a shop where we want to create popular \textbf{Bundle Deals}.
    \vfill
    \begin{itemize}
        \item \textbf{Receipts:} Each list represents one customer visit.
        \item \textbf{Rule:} Customers buy at most \textit{one} of each item.
        \item \textbf{Popularity Threshold ($minsup$):} We only keep bundles appearing in $\ge \sigma\%$ of receipts.
    \end{itemize}
    \vfill
    \begin{block}{The Logic}
        If \textbf{Coffee} is unpopular, any bundle containing Coffee is also unpopular. This allows us to "Prune" the search space.
    \end{block}
\end{frame}

\section{The Distributed Wall}
\begin{frame}{Spark RDD Bottlenecks}
    In a Spark cluster, data is partitioned. 
    \vfill
    \begin{itemize}
        \item Workers must match millions of candidates against local receipts.
        \item \alert{The Problem:} Standard search structures (Hash Trees) fail to scale.
        \item \textbf{The Solution:} Moving towards \textbf{Hash Table Tries} for $O(1)$ child lookups.
    \end{itemize}
\end{frame}

\end{document}
